Constrained Optimization-Based Neuro-Adaptive Control (CoNAC) for Uncertain Euler-Lagrange Systems Under Weight and Input Constraints

### 2025-04-12 manuscript.tex
finalize sim reulst

\begin{itemize}
    \item $\otimes$ denotes the Kronecker product \cite[Definition 7.1.2]{Bernstein:2009aa}.
    \item $\mv x=[x_i]_{i\in[1,\cdots,n]}\in\R^n$ and $
        \mm A
        := 
        [a_{ij}]
        _{
            i\in[1,\cdots,n],j\in[1,\cdots ,m]
        }\allowbreak\in\R^{n\times m}
        $ denote a vector and a matrix.
    \item $\myrow_i(\mm A)$ denotes the $i\textsuperscript{th}$ row of the matrix $\mm A\in\R^{n\times m}$. 
    \item $\myvec(\mm A):= [\myrow_1(\mm A^\top)  ,\cdots,\myrow_m(\mm A^\top)  ]^\top   $ for $\mm A\in\R^{n\times m}$.
    % \item $\mycol_i(A)$ and $\myrow_j(A)$ denote the $i\textsuperscript{th}$ column and $j\textsuperscript{th}$ row of $A\in\R^{n\times m}$, respectively.
    % \item $\myvec(A):= [\mycol_1(A)^\top  ,\cdots,\mycol_m(A)^\top  ]^\top   $ for $A\in\R^{n\times m}$.
    \item $\lambda_{\min}(\mm A)$ denotes the minimum eigenvalue of the matrix $\mm A\in\R^{n\times n}$.
    \item $\mm I_n$ denotes the $n\times n$ identity matrix.
\end{itemize}

@@

Consider the Lyapunov function $V_1:= \tfrac{1}{2}\fe^\top \rbM\fe$. 
Invoking Property \ref{prop:skew}, the time derivative of $V_1$ is
\begin{equation}
    \begin{aligned}
        \ddtt{V}_1
        =&
        \fe^\top \rbM (
            -\rbVm \fe -\mm K \fe + \mv f
            -\rbd + \mysat(\rbu)
        )
        \\
        &
        +
        \tfrac{1}{2}
        \fe^\top \dot{\rbM}\fe
        \\
        =&
        -
        \fe^\top \mm K \fe 
        +
        \fe^\top (
            \mv f+\mysat(\rbu)
            -\rbd
        )
        \\
        &
        +
        \tfrac{1}{2}
        \fe^\top(\dot{\rbM}- 2\rbVm)\fe
        \\
        \le&
        -\lambda_{\min}(\mm K)\norm{\fe}^2
        +
        \overline\tau_d\norm{\fe}
        +
        \fe^\top (\mv f+\mysat(\rbu))
        \\
        \le&
        -\lambda_{\min}(\mm K)\norm{\fe}^2
        +
        \overline\tau_d\norm{\fe}
        +
        \fe^\top (\mysat(\rbu)-\rbu^*)
        ,
    \end{aligned}
    \label{eq:lya1:dot1}
\end{equation}
where $\rbu^*:= -\mv f$ is the ideal control input whose maximum norm is $\overline\tau$ according to Assumption \ref{assum:feasible} and $\mysat(\cdot)$. 
Therefore, one can conclude that $\fe$ is exponentially stable so that $\lim_{t\to\infty}\norm{\fe}=\tfrac{\overline\tau_d}{\lambda_{\min}(\mm K)}$, if $\rbu=-\rbu^*$ can be realized.
However, $\rbu^*$ is not available in practice, since $\mv f$ is unknown.

@@

The proposed CoNAC was validated via numerical simulations and real-time experiments on a two-link manipulator.

@@

% ------------------------------------
% MCU & Robot Model and Ref. Trajectory
% ------------------------------------
The proposed CoNAC was implemented using the OpenCR1.0 \cite{opencr} with a 32-bit ARM Cortex and a 216 MHz clock frequency.
The two-link manipulator model is depicted in Fig.~\ref{fig: manipulator}, adapted from \cite{Markus:2013aa}. 
\MSRY{CORRECT HERE}
The system dynamics of the two-link manipulator is described in \eqref{eq:sys1}, and for the numerical validation, the parameters are assumed to be constant such that $\rbM=\mydiag([m_1,m_2])$, $\rbVm=\mydiag([b_1,b_2])$, and $\rbF=\mydiag([f_{c_1},f_{s_1},f_{c_2},f_{s_2}])$,
where the parameters $q_p,{q_d}_p,\tau_p,m_p,l_p,{l_c}_p,b_p,{f_c}_p$ and ${f_s}_p$ denote the joint angle, desired joint angle, torque, mass, length, center of mass, viscous friction coefficient, coulomb friction coefficient, and static friction coefficient, respectively, for link $p\in[1,2]$.
The values of the system model parameters are provided in Table~\ref{table:system:params}.

% ------------------------------------
% Robot Model Figure and Table
% ------------------------------------
\begin{figure}[t]
    \centering
    \includegraphics[width=0.75\linewidth]{fig/RobotModel.drawio.png}
    \caption{Two-link manipulator model.}
    \label{fig: manipulator}
\end{figure}

\begin{table}[t]
    \renewcommand{\arraystretch}{1.3}
    \caption{Two-link manipulator parameters of $p\textsuperscript{th}$ link.}
    \centering
    \begin{tabular}{c m{6.5em} c c c }
    % \begin{tabular}{c c c c c}
    \hline
    \textbf{Symbol} & \textbf{Description} & \textbf{Link 1} & \textbf{Link 2} \\
    \hline
    \hline 
    $m_p$ & Mass & 2.465 (kg) & 2.465 (kg) \\
    \hline
    $l_p$  & Length & 0.2 (m) & 0.18 (m) \\
    \hline
    ${l_c}_p$ & Center of mass & 0.139 (m) & 0.087 (m) \\
    \hline
    $b_p$   & Viscous friction coef. &  0.1 (Nms) & 0.1 (Nms) \\
    \hline
    ${f_c}_p$  & Coulomb friction coef. &  0.24 (Nm) & 0.24 (Nm) \\
    \hline
    ${f_s}_p$  & Static friction coef. &  0.3 (Nm) & 0.2 (Nm) \\
    \hline
    $I_p$  & Inertia & 0.069 (kgm\textsuperscript{2}) & 0.015 (kgm\textsuperscript{2}) \\
    \hline
    \end{tabular}
    \label{table:system:params}
\end{table}

% ------------------------------------
% Reference Trajectory
% ------------------------------------
The desired trajectory for $\q=[q_1,q_2]^\top $ was generated using fifth-order polynomial functions $\mypoly^5(\mv{x}_1,\mv{x}_2,t_f,t)$, to satisfy the initial $\mv{x}_1$ and final $\mv{x}_2$ angle conditions and zero velocities of the joints, where $t_f$ is the time duration.
The desired trajectory is defined as follows:
\begin{equation}
    \qd(t) 
    \!=\! 
    \begin{bmatrix}
        {q_d}_1\\{q_d}_2
    \end{bmatrix}
    \!=\!
    \begin{cases}
    \mypoly^5({\qd}_0,{\qd}_1,t_f,t),
        \!&\!
        \text{if } 0\le t < t_f 
        ,
        \\
    \mypoly^5({\qd}_1,{\qd}_2,t_f,t-t_f),
        \!&\!
        \text{if } t_f\le t < 2t_f 
        ,
        \\
    \mypoly^5({\qd}_2,{\qd}_1,t_f,t-2t_f),
        \!&\! 
        \text{if } 2t_f\le t < 3t_f 
        .
        \\
    \mypoly^5({\qd}_1,{\qd}_0,t_f,t-3t_f),
        \!&\!    
        \text{if } 3t_f\le t < 4t_f 
        ,
        \\
    \end{cases}
    \label{eq:desired trajectory}
\end{equation}
where ${\qd}_0:=\left(-\tfrac{1}{2}\pi,0\right)^\top$, ${\qd}_1:=\left(\tfrac{1}{4}\pi,-\tfrac{5}{4}\pi\right)^\top$, ${\qd}_2:=\left(-\tfrac{1}{4}\pi,\tfrac{1}{4}\pi\right)^\top$, and $t_f=3$ s.
To demonstrate the learning capability of NN, the desired trajectory was applied twice; let us call the first and second iterations of the reference trajectory as Episode $1$ and Episode $2$, respectively.

@@

% ------------------------------------
% Control Input Saturation
% ------------------------------------
To demonstrate the effectiveness of the proposed CoNAC to handle the combination of the convex input constraints, the saturation function is defined to satisfy the following domain $\Theta_{\mysat}:=\left\{\Theta_{\mysat, {\rbu}}\cap\Theta_{\mysat, {\tau_2}}\right\}$ as depicted in Fig.~\ref{fig:sat}, where
%
\begin{subequations}
    \begin{align}
        \Theta_{\mysat, {\rbu}}
        :=&
        \left\{
            \rbu
            \mid
            \norm{\rbu} \le 
            10
            % \overline\tau
        \right\}
        \label{eq:sat:norm}
        ,
        \\
        \Theta_{\mysat, {\tau_2}}
        :=&
        \left\{
            \tau_2
            \mid
            \vert{\tau_2}\vert \le 
            2.5
            % \overline\tau_2
        \right\}
        .
        \label{eq:sat:tau2}
    \end{align}
    \label{eq:sat}
\end{subequations}
%
These domains \eqref{eq:sat:norm} and \eqref{eq:sat:tau2} can be physically interpreted as a combination of the voltage source limitation of the actuators and the torque limitation of the second link actuator.

\begin{figure}[t]
    \centering
    \includegraphics[width=0.45\linewidth]{
        src/figures/saturation.drawio.pdf
    }
    \caption{Control input saturation function.}
    \label{fig:sat}
\end{figure}

@@

% ------------------------------------
% Controllers
% ------------------------------------
For a comparative study, we implemented 3 controllers:

% ------------------------------------
% Controllers: CoNAC 
% ------------------------------------
\subsubsection*{Controller 1: (C$_1$) proposed}

To handle the input saturation, the proposed CoNAC was implemented with the input bound constraint for second link $c_{\overline\tau_2}$ and $c_{\underline\tau_2}$ \eqref{eq:cstr:input:bound} and the nonlinear input norm constraint $c_{\rbu}$ \eqref{eq:cstr:input:norm}, as follows:
\begin{equation}
    \begin{aligned}
        c_{\overline\tau_2}     
        =&
        \tau_2-\overline\tau_2
        \le 0
        ,
        \quad
        c_{\underline\tau_2} 
        =&
        \underline\tau_2-\tau_2
        \le 0
        ,
        \quad
        c_{\rbu}
        =&
        \tfrac{1}{2}
        (
            \norm{\rbu}-\overline\tau
        )^2 
        ,
    \end{aligned}
    \label{eq:sim:cstr:CoNAC}
\end{equation}
where $\overline\tau_2=2.5$ and $\underline\tau_2=-2.5$ are the upper and lower bounds of the second link actuator, respectively, and $\overline\tau=10$ is the maximum allowable norm of the control input.
Hence, (C$_1$) is possible to use full capability of the actuator.
The weight constraints $c_{\theta_i},\ \forall i\in[0,\cdots,k]$ were also considered in the CoNAC.
As described in \eqref{eq:control:est}, the control input is equal to the output of the NN $\rbu$, and the adaptation law is defined in \eqref{eq:adaptation law}.

@@

On the other hand, the existing auxiliary system \cite{Esfandiari:2014aa,Karason:1994aa,Esfandiari:2015aa} was used to compare with the proposed (C$_1$).
The auxiliary system is defined as $\ddtt{\mv\zeta} = \mm{A}_\zeta \mv{\zeta} + \mm{B}_\zeta \Delta\tau_{1},\ \mv{\zeta}\vert_{t=0} = 0$, where $\mv{\zeta}\in\R^n$ denotes the auxiliary state, $\mm{A}_\zeta\in\R_{<0}^{n\times n}$ and $\mm{B}_\zeta\in\R^{n\times n}$, and $\Delta\tau_{1} = 
\tau_{1}-\max(\underline\tau_1,\min(\overline\tau_1,\tau_1))$.
Since, the auxiliary system only considers the input bound constraint, $\overline{\tau}_1$ is set to $9.682$ to approximately match the maximum allowable norm of the control input $\overline\tau$, \ie $\overline{\tau}_1^2+\overline{\tau}_2^2=\overline{\tau}^2$.

The auxiliary state variables were used in the adaptation law \eqref{eq:adap:th:approx} by substituting $\fe$ with $\fe+\mv{\zeta}$.
Hence, the weights are adapted to reduce not only the tracking error $\fe$ but also the auxiliary state $\mv{\zeta}$.

@@

To investigate the effect of the update rate of Lagrange multipliers, C$_3$ was implemented with small $\beta_i$ values.

@@

% ------------------------------------
% Controller Parameters
% ------------------------------------
For all controllers ((C$_1$), (C$_2$), and (C$_3$)), the NN input vector ${\q}_n$ was set as ${\q}_n=\left(\q^\top,\dq^\top,\fe^\top,1\right)^\top\in\R^{3n+1}$ with the augmented scalar $1$ included to account for the bias term in the weight matrix. 
The NNs' weights were initialized randomly with uniform distribution in the range of $[-0.1,0.1]$.
Each NN architecture had two hidden layers with eight nodes (\ie $k=2, l_0=6, l_1=4, l_2=4, l_3=2$), and the adaptation gain was set to $\alpha=0.5$.
The filtering matrix $\mm{\Lambda}$ was set to $\mm{\Lambda}=\mydiag([5,15])$.
The sampling rate of the controller was $250$ Hz, and $1000$ Hz for the simulation.
To emphasize the control input constraint handling capability, the weight constraint parameters were selected sufficiently large (\ie $\overline\wth_0=11, \overline\wth_1=12$, and $\overline\wth_2=13$), avoiding the violation of the weight constraints. 
The readers are referred to the other papers of the author's \MSRY{ECC, IECON paper} for the demonstration of the capabilities of the proposed CoNAC to handle the weight constraints.

The quantitative comparison of the tracking performance was evaluated using the $L_2$-norm of them, (\ie $\sqrt{\int_0^T\norm{h},\der t}$, where $h\in\{r_1,r_2\}$ and $T\in\R_{>0}$ denotes the episode duration time.
Note that $c_{\overline\tau_i}$ and $c_{\underline\tau_i},\ \forall i\in\{1,2\}$ can not be active at the same time.

% ------------------------------------
% Controller Table
% ------------------------------------
\begin{table}[t]
    \renewcommand{\arraystretch}{1.3}
    \caption{Properties of the controllers used in simulation}
    \label{table:controller}
    \centering
    \begin{tabular}{c l l}
    \hline
        \!&\!\bf{Description}\!&\!\bf{Input Constraint}\!\\
    \hline
    \hline
        (C$_1$) & proposed & $\overline{\tau}=10$ and $\overline{\tau}_2=-\underline{\tau}_2=2.5$ \\
    \hline
        (C$_2$) & aux. sys. & $\overline{\tau}_1=-\underline{\tau}_1=9.682$ and $\overline{\tau_2}=-\underline{\tau_2}=2.5$ \\
    \hline
        (C$_3$) & small $\beta_i$ & $\overline{\tau}=10$ and $\overline{\tau}_2=-\underline{\tau_2}=2.5$ \\
    \hline
    \end{tabular}
\end{table}

@@

\begin{figure*}[t]
  \centering
    \subfloat[Tracking result of $q_1$.]{
      \includegraphics[width=\figSizeTwoCol\linewidth]
      {
        % src/script_simulation/figures/compare/Fig10.eps
        src/script_simulation/figures/compare/Fig1.eps
      }%
      \label{fig:ctrl:result:q1}}
    \hfill
    \subfloat[Tracking result of $q_2$.]{
      \includegraphics[width=\figSizeTwoCol\linewidth]
      {
        % src/script_simulation/figures/compare/Fig11.eps
        src/script_simulation/figures/compare/Fig2.eps
      }%
      \label{fig:ctrl:result:q2}}
    \vfill
      \subfloat[Control input $\tau_1$.]{
        \includegraphics[width=\figSizeTwoCol\linewidth]
        {
            src/script_simulation/figures/compare/Fig3.eps
        }%
        \label{fig:ctrl:result:tau:1}}
    \hfill
      \subfloat[Control input $\tau_2$.]{
        \includegraphics[width=\figSizeTwoCol\linewidth]
        {
            src/script_simulation/figures/compare/Fig4.eps
        }%
        \label{fig:ctrl:result:tau:2}}
        \vfill
    \subfloat[Norm of control input $\tau$.]{
        \includegraphics[width=\figSizeTwoCol\linewidth]
        {
            src/script_simulation/figures/compare/Fig5.eps
        }%
        \label{fig:ctrl:result:tau:norm}}
    \hfill
    \subfloat[Norm of weights $\hat\theta_i$.]{
        \includegraphics[width=\figSizeTwoCol\linewidth]
        {
            src/script_simulation/figures/compare/Fig7.eps
        }%
        \label{fig:ctrl:result:weight}}        
    \caption{
  Simulation results of the (C$_1$) (blue), (C$_2$) (cyan), (C$_3$) (gray), and reference signal of $\qd$ (red dashed line).
  }
\label{fig:ctrl:result}
\end{figure*}

>>>>

\begin{itemize}
    \item $\otimes$ denotes the Kronecker product \cite[Definition 7.1.2]{Bernstein:2009aa}.
    \item $\mv x=[x_i]_{i\in[1,\cdots,n]}\in\R^n$ and $
        \mm A
        := 
        [a_{ij}]
        _{
            i\in[1,\cdots,n],j\in[1,\cdots ,m]
        }\allowbreak\in\R^{n\times m}
        $ denote a vector and a matrix.
    \item $\myrow_i(\mm A)$ denotes the $i\textsuperscript{th}$ row of the matrix $\mm A\in\R^{n\times m}$. 
    \item $\myvec(\mm A):= [\myrow_1(\mm A^\top)  ,\cdots,\myrow_m(\mm A^\top)  ]^\top   $ for $\mm A\in\R^{n\times m}$.
    % \item $\mycol_i(A)$ and $\myrow_j(A)$ denote the $i\textsuperscript{th}$ column and $j\textsuperscript{th}$ row of $A\in\R^{n\times m}$, respectively.
    % \item $\myvec(A):= [\mycol_1(A)^\top  ,\cdots,\mycol_m(A)^\top  ]^\top   $ for $A\in\R^{n\times m}$.
    \item $\lambda_{\min}(\mm A)$ denotes the minimum eigenvalue of the matrix $\mm A\in\R^{n\times n}$.
    \item $\mm I_n$ denotes the $n\times n$ identity matrix, and $\mm 0_{n\times m}$ denotes the $n\times m$ zero matrix.
\end{itemize}

@@

Consider the Lyapunov function $V_1:= \tfrac{1}{2}\fe^\top \rbM\fe$. 
Invoking Property \ref{prop:skew}, the time derivative of $V_1$ is
\begin{equation}
    \begin{aligned}
        \ddtt{V}_1
        =&
        \fe^\top \rbM (
            -\rbVm \fe -\mm K \fe + \mv f
            -\rbd + \mysat(\rbu)
        )
        \\
        &
        +
        \tfrac{1}{2}
        \fe^\top \dot{\rbM}\fe
        \\
        =&
        -
        \fe^\top \mm K \fe 
        +
        \fe^\top (
            \mv f+\mysat(\rbu)
            -\rbd
        )
        \\
        &
        +
        \tfrac{1}{2}
        \fe^\top(\dot{\rbM}- 2\rbVm)\fe
        \\
        \le&
        -\lambda_{\min}(\mm K)\norm{\fe}^2
        +
        \overline\tau_d\norm{\fe}
        +
        \fe^\top (\mv f+\mysat(\rbu))
        \\
        \le&
        -\lambda_{\min}(\mm K)\norm{\fe}^2
        +
        \overline\tau_d\norm{\fe}
        +
        \fe^\top (\mysat(\rbu)-\rbu^*)
        ,
    \end{aligned}
    \label{eq:lya1:dot1}
\end{equation}
where $\rbu^*:= -\mv f$ is the ideal control input whose maximum norm is $\overline\tau$ according to Assumption \ref{assum:feasible} and $\mysat(\cdot)$. 
Therefore, one can conclude that $\fe$ is exponentially stable so that $\lim_{t\to\infty}\norm{\fe}=\tfrac{\overline\tau_d}{\lambda_{\min}(\mm K)}$, if $\rbu=-\rbu^*$ can be realized.
However, $\rbu^*$ is not available in practice, since $\mv f$ is unknown.
\MSRY{여기서는 MVT, IFT을 사용하지 않았기 때문에 아이디얼 제어가 포화되지 않을 필요성이 없다. 실험에서도 포화를 핸들링하는 중에 추종이 완벽히 되지 못하는 것을 보인다.}

@@

The proposed CoNAC was validated via numerical simulation and real-time experiment on a two-link manipulator.

@@

% ------------------------------------
% MCU & Robot Model and Ref. Trajectory
% ------------------------------------
The two-link manipulator model is depicted in Fig.~\ref{fig:robot:model}, adapted from \cite{Markus:2013aa}. 
\MSRY{CORRECT HERE}
The system dynamics of the two-link manipulator is described in \eqref{eq:sys1}, and for the numerical validation, the parameters are assumed to be constant such that $\rbM=\mydiag([m_1,m_2])$, $\rbVm=\mydiag([b_1,b_2])$, and $\rbF=\mydiag([f_{c_1},f_{s_1},f_{c_2},f_{s_2}])$,
where the parameters $q_p,{q_d}_p,\tau_p,m_p,l_p,{l_c}_p,b_p,{f_c}_p$ and ${f_s}_p$ denote the joint angle, desired joint angle, torque, mass, length, center of mass, viscous friction coefficient, coulomb friction coefficient, and static friction coefficient, respectively, for link $p\in[1,2]$.
The values of the system model parameters are provided in Table~\ref{table:system:params}.

% ------------------------------------
% Robot Model Figure and Table
% ------------------------------------
\begin{figure}[t]
    \centering
    \subfloat[Two-link manipulator model.]{
        \includegraphics[width=0.75\linewidth]{src/figures/RobotModel.drawio.pdf}
        \label{fig:robot:model}
    }
    \hfill
    \subfloat[Control input saturation function.\MSRY{sat이 아니라 집합으로 표현하기}]{
        \includegraphics[width=0.45\linewidth]{src/figures/saturation.drawio.pdf}
        \label{fig:robot:sat}
    }
    \caption{Two-link manipulator model and control saturation function.}
    \label{fig:robot}
\end{figure}

% ------------------------------------
% Robot Model Parameters
% -----------------------------------
\begin{table}[t]
    \renewcommand{\arraystretch}{1.3}
    \caption{Two-link manipulator parameters of $p\textsuperscript{th}$ link.}
    \centering
    \begin{tabular}{c m{6.5em} c c c }
    % \begin{tabular}{c c c c c}
    \hline
    \textbf{Symbol} & \textbf{Description} & \textbf{Link 1} & \textbf{Link 2} \\
    \hline
    \hline 
    $m_p$ & Mass & 2.465 (kg) & 2.465 (kg) \\
    \hline
    $l_p$  & Length & 0.2 (m) & 0.18 (m) \\
    \hline
    ${l_c}_p$ & Center of mass & 0.139 (m) & 0.087 (m) \\
    \hline
    $b_p$   & Viscous friction coef. &  0.1 (Nms) & 0.1 (Nms) \\
    \hline
    ${f_c}_p$  & Coulomb friction coef. &  0.24 (Nm) & 0.24 (Nm) \\
    \hline
    ${f_s}_p$  & Static friction coef. &  0.3 (Nm) & 0.2 (Nm) \\
    \hline
    $I_p$  & Inertia & 0.069 (kgm\textsuperscript{2}) & 0.015 (kgm\textsuperscript{2}) \\
    \hline
    \end{tabular}
    \label{table:system:params}
\end{table}

% ------------------------------------
% Reference Trajectory
% ------------------------------------
The desired trajectory for $\q=[q_1,q_2]^\top $ was generated using fifth-order polynomial functions $\mypoly^5(\mv{x}_1,\mv{x}_2,t_f,t)$, to satisfy the initial $\mv{x}_1$ and final $\mv{x}_2$ angle conditions and zero velocities of the joints, where $t_f$ is the time duration.
The desired trajectory is defined as follows:
\begin{equation}
    \qd(t) 
    \!=\! 
    \begin{bmatrix}
        {q_d}_1\\{q_d}_2
    \end{bmatrix}
    \!=\!
    \begin{cases}
    \mypoly^5({\qd}_0,{\qd}_1,t_f,t),
        \!&\!
        \text{if } 0\le t < t_f 
        ,
        \\
    \mypoly^5({\qd}_1,{\qd}_2,t_f,t-t_f),
        \!&\!
        \text{if } t_f\le t < 2t_f 
        ,
        \\
    \mypoly^5({\qd}_2,{\qd}_1,t_f,t-2t_f),
        \!&\! 
        \text{if } 2t_f\le t < 3t_f 
        .
        \\
    \mypoly^5({\qd}_1,{\qd}_0,t_f,t-3t_f),
        \!&\!    
        \text{if } 3t_f\le t < 4t_f 
        ,
        \\
    \end{cases}
    \label{eq:desired trajectory}
\end{equation}
where ${\qd}_0:=\left(-\tfrac{1}{2}\pi,0\right)^\top$, ${\qd}_1:=\left(\tfrac{1}{4}\pi,-\tfrac{1}{2}\pi\right)^\top$, ${\qd}_2:=\left(-\tfrac{1}{4}\pi,\tfrac{1}{4}\pi\right)^\top$, and $t_f=3$ s.
To demonstrate the learning capability of NN, the desired trajectory was applied twice; let us call the first and second iterations of the reference trajectory as Episode $1$ and Episode $2$, respectively.

@@

% ------------------------------------
% Control Input Saturation
% ------------------------------------
To demonstrate the effectiveness of the proposed CoNAC to handle the combination of the convex input constraints, the saturation function is defined to project the control input onto following convex domain $\Theta_{\mysat}:=\left\{\Theta_{\mysat, {\rbu}}\cap\Theta_{\mysat, {\tau_2}}\right\}$ as depicted in Fig.~\ref{fig:robot:sat}, where
%
\begin{subequations}
    \begin{align}
        \Theta_{\mysat, {\rbu}}
        :=&
        \left\{
            \rbu
            \mid
            \norm{\rbu} \le 
            10
            % \overline\tau
        \right\}
        \label{eq:sat:norm}
        ,
        \\
        \Theta_{\mysat, {\tau_2}}
        :=&
        \left\{
            \tau_2
            \mid
            \vert{\tau_2}\vert \le 
            2.5
            % \overline\tau_2
        \right\}
        .
        \label{eq:sat:tau2}
    \end{align}
    \label{eq:sat}
\end{subequations}
%
These domains \eqref{eq:sat:norm} and \eqref{eq:sat:tau2} can be physically interpreted as a combination of the voltage source limitation of the actuators and the torque limitation of the second link actuator, respectively.

@@

% ------------------------------------
% Comparative Study
% ------------------------------------
For a comparative study, we implemented 3 controllers.
The properties of the controllers are summarized in Table~\ref{table:controllers}.

% ------------------------------------
% Controllers: CoNAC 
% ------------------------------------
\subsubsection*{Controller 1: (C$_1$) CoNAC; proposed}

To handle the input saturation, the proposed CoNAC was implemented with the input bound constraint for second link $c_{\overline\tau_2}$ and $c_{\underline\tau_2}$ \eqref{eq:cstr:input:bound} and the nonlinear input norm constraint $c_{\rbu}$ \eqref{eq:cstr:input:norm}, as follows:
\begin{equation}
    c_{\overline\tau_2}     
    =
    \tau_2-\overline\tau_2
    \le 0
    ,
    \;
    c_{\underline\tau_2} 
    =
    \underline\tau_2-\tau_2
    \le 0
    ,
    \;
    c_{\rbu}
    =
    \tfrac{1}{2}
    (
        \norm{\rbu}-\overline\tau
    )^2 
    <0
    ,
    \label{eq:sim:cstr:CoNAC}
\end{equation}
where $\overline\tau_2=-\underline{\tau}_2=2.5$ are the absolute bound of the second link actuator, and $\overline\tau=10$ is the maximum feasible norm of the control input.
Hence, (C$_1$) is possible to use full capability of the actuator.
The weight constraints $c_{\theta_i},\ \forall i\in[0,\cdots,k]$ were also considered in the CoNAC.
As described in \eqref{eq:control:est}, the control input is equal to the output of the NN, and the adaptation law is defined in \eqref{eq:adaptation law}.

The update rate of the Lagrange multipliers was set to $\beta_{\theta_i}=10^{-3},\ \forall i\in[0,\cdots,k]$, and $\beta_{\rbu}=10$ and $\beta_{\overline{\tau}_2}=\beta_{\underline{\tau}_2}=10^{3}$.

@@

On the other hand, the existing auxiliary system \cite{Esfandiari:2014aa,Karason:1994aa,Esfandiari:2015aa} was used to compare with the proposed (C$_1$).
The auxiliary system is defined as $\ddtt{\mv\zeta} = \mm{A}_\zeta \mv{\zeta} + \mm{B}_\zeta \Delta\rbu,\ \mv{\zeta}\vert_{t=0} = \mv{0}_{2\times1}$, where $\mv{\zeta}\in\R^n$ denotes the auxiliary state, $\mm{A}_\zeta\in\R_{<0}^{n\times n}$, and $\mm{B}_\zeta\in\R^{n\times n}$.
The auxiliary state $\mv{\zeta}$ is affected by the saturated control input $\Delta\rbu$, whose entry is defined as $\Delta\tau_{i} = 
\tau_{i}-\max(\underline\tau_i,\min(\overline\tau_i,\tau_i)),\ \forall i\in\{1,2\}$.
Since, the auxiliary system only considers the input bound constraint, $\overline{\tau}_1$ is set to $9.682$ to approximately match the maximum allowable norm of the control input $\overline\tau$, (\ie $\overline{\tau}_1^2+\overline{\tau}_2^2=\overline{\tau}^2$, and $\overline{\tau}_2=2.5$ and $\overline{\tau}=10$).

The auxiliary state are used in the adaptation law \eqref{eq:adap:th:approx} by substituting $\fe$ with $\fe+\mv{\zeta}$.
Hence, the weights are adapted to reduce not only the tracking error $\fe$ but also the auxiliary state $\mv{\zeta}$.

The matrices of the auxiliary system are set to $\mm{A}_\zeta=\mydiag([-10,-10])$ and $\mm{B}_\zeta=\mydiag([10^3,10^3])$, considering the tradeoff between the sensitivity of the control saturation, and the convergence speed.
\MSRY{sensitivity와 convergence에 대해서 더 설명이 필요한가?}

@@

To investigate the effect of the update rate of Lagrange multipliers, (C$_3$) was implemented with small $\beta_i$ values, which are set to $\beta_{\rbu}=1$, and $\beta_{\overline{\tau}_2}=\beta_{\underline{\tau}_2}=10^{2}$.
The remaining parameters are the same as (C$_1$).

@@

% ------------------------------------
% Controller Parameters
% ------------------------------------
For all controllers ((C$_1$), (C$_2$), and (C$_3$)), the NN input vector ${\q}_n$ was set as ${\q}_n=\left(\q^\top,\dq^\top,\fe^\top,1\right)^\top\in\R^{3n+1}$ with the augmented scalar $1$ included to account for the bias term in the weight matrix. 
The NNs' weights were initialized randomly with uniform distribution in the range of $[-0.1,0.1]$, and the same random seed.
Each NN architecture had two hidden layers with four nodes (\ie $k=2, l_0=6, l_1=4, l_2=4, l_3=2$), and the adaptation gain was set to $\alpha=0.5$.
The filtering matrix $\mm{\Lambda}$ was set to $\mm{\Lambda}=\mydiag([5,15])$.
The sampling rate of the controller was $250$ Hz considering the further real-time implementation, and $1000$ Hz for the simulation.
To emphasize the control input constraint handling capability, the weight constraint parameters were selected sufficiently large (\ie $\overline\wth_0=11, \overline\wth_1=12$, and $\overline\wth_2=13$), avoiding the violation of the weight constraints. 
The readers are referred to the previous papers of the author's \MSRY{ECC, IECON paper} for the demonstration of the capabilities of the proposed CoNAC to address the weight constraints.

The quantitative comparison of the tracking performance was evaluated using the $L_2$-norm of them, (\ie $\sqrt{\int_0^T\norm{h}\,\der t}$, where $h\in\{r_1,r_2\}$ and $T\in\R_{>0}$ denotes the each episode duration time.

% ------------------------------------
% Controller Table
% ------------------------------------
\begin{table}[t]
    \renewcommand{\arraystretch}{1.3}
    \caption{Properties of the controllers used in simulation}
    \label{table:controller}
    \centering
    \begin{tabular}{c l l}
    \hline
        \!&\!\bf{Description}\!&\!\bf{Input Constraint}\!\\
    \hline
    \hline
        (C$_1$) & proposed & $\overline{\tau}=10$ and $\overline{\tau}_2=-\underline{\tau}_2=2.5$ \\
    \hline
        (C$_2$) & aux. sys. & $\overline{\tau}_1=-\underline{\tau}_1=9.682$ and $\overline{\tau_2}=-\underline{\tau_2}=2.5$ \\
    \hline
        (C$_3$) & small $\beta_i$ & $\overline{\tau}=10$ and $\overline{\tau}_2=-\underline{\tau_2}=2.5$ \\
    \hline
    \end{tabular}
    \label{table:controllers}
\end{table}

@@

\begin{figure*}[t]
  \centering
    \subfloat[Tracking result of $q_1$.]{
      \includegraphics[width=\figSizeTwoCol\linewidth]
      {
        % src/script_simulation/figures/compare/Fig10.eps
        src/script_simulation/figures/compare/Fig1.eps
      }%
      \label{fig:ctrl:result:q1}}
    \hfill
    \subfloat[Tracking result of $q_2$.]{
      \includegraphics[width=\figSizeTwoCol\linewidth]
      {
        % src/script_simulation/figures/compare/Fig11.eps
        src/script_simulation/figures/compare/Fig2.eps
      }%
      \label{fig:ctrl:result:q2}}
    \vfill
      \subfloat[Control input $\tau_1$.]{
        \includegraphics[width=\figSizeTwoCol\linewidth]
        {
            src/script_simulation/figures/compare/Fig3.eps
        }%
        \label{fig:ctrl:result:tau:1}}
    \hfill
      \subfloat[Control input $\tau_2$.]{
        \includegraphics[width=\figSizeTwoCol\linewidth]
        {
            src/script_simulation/figures/compare/Fig4.eps
        }%
        \label{fig:ctrl:result:tau:2}}
        \vfill
    \subfloat[Norm of control input $\tau$.]{
        \includegraphics[width=\figSizeTwoCol\linewidth]
        {
            src/script_simulation/figures/compare/Fig5.eps
        }%
        \label{fig:ctrl:result:tau:norm}}
    \hfill
    \subfloat[Norm of weights $\hat\theta_i$.]{
        \includegraphics[width=\figSizeTwoCol\linewidth]
        {
            src/script_simulation/figures/compare/Fig7.eps
        }%
        \label{fig:ctrl:result:weight}}        
    \caption{
  Simulation results of (C$_1$) (blue), (C$_2$) (cyan), (C$_3$) (gray), and reference signal of $\qd$ (red dashed line).
  }
\label{fig:ctrl:result}
\end{figure*}

\begin{figure}[t]
    \centering
    \subfloat[Control input $\tau$ in time interval from $19$ s to $21$ s (bird's eye view).]{
    % \subfloat[Auxiliary states $\mv{\zeta}$ of CoNAC-AUX.]{
        \includegraphics[width=\figSizeOneCol\linewidth]
        {
            src/script_simulation/figures/compare/Fig6.eps
        }%
        \label{fig:ctrl:result:scope:control}}
        \vfill
    \subfloat[Lagrange multipliers $\lambda_j$  in time interval from $19$ s to $21$ s.]{
        \includegraphics[width=\figSizeOneCol\linewidth]
        {
            src/script_simulation/figures/compare/Fig8.eps
        }%
        \label{fig:ctrl:result:scope:beta}}
        \vfill
    \subfloat[Auxiliary states in time interval from $19$ s to $21$ s.]{
        \includegraphics[width=\figSizeOneCol\linewidth]
        {
            src/script_simulation/figures/compare/Fig9.eps
        }%
        \label{fig:ctrl:result:scope:aux}}
  \caption{
    Constraint handling process of (C$_1$) (blue), (C$_2$) (cyan), and (C$_3$) (gray) in time interval from $19$ s to $21$ s.
  }
\label{fig:ctrl:result:scope}
\end{figure}
